The Concurrent Calculi Formalisation Benchmark

### 2024-02-22 short-paper/short-paper.tex
Shorten the scope extrusion related work section.

This is the challenge most closely related to  POPLMark,
since it concerns the properties of binders, whose encoding has been
extensively studied with respect to the $\lambda$-calculi. Process calculi
present additional challenges,  typically including several
different binding constructs: inputs bind a received name or value,
recursive processes bind recursion variables, and restrictions bind
names.  The first two act similarly to the binders known from
$\lambda$-calculi, but restrictions may be more challenging due to
scope extrusion.

Given those peculiarities, the syntax and semantics of $\pi$-calculi have been
mechanised from an early age (see~\cite{Melham1994}) with many proof
assistants and in so many encoding styles that it would take too long to
review.  They range from concrete encodings based on named syntax
\cite{Melham1994} to basic de Bruijn~\cite{Hirschkoff1997, Perera2018} and locally nameless
representation %~\cite{Chargueraud2012}
(\eg~\cite{Castro2020}).
Nominal approaches are also common (see~\cite{Bengtson2009}), but they
may be problematic in proof assistants based on dependent types.

\todo{Sum up some of those issues}
% \cite{Maksimovic2015} does not have
% name restriction, thus dodging the challenge of scope extrusion.
\begin{quotation}
\cite{Castro-Perez2021,Castro2020} note that popular presentations of
session type systems are impossible to directly encode using
intrinsically \(\alpha\)-convertible terms.  \cite{Castro2020}
suggests using several binder constructs to solve this, but notes that
this requires proving many variants of the same theorems.
The case study \cite{AmbalLS21} compares four approaches to encoding
binders in Coq as a first step towards developing tools for working
with higher-order process calculi.  They found that working directly
with de Bruijn indices was easiest and shortest since the existing
approaches developed for $\lambda$-calculus binders do not work well
with scope extrusion.  Specifically, the locally nameless
representation~\cite{Chargueraud2012} cannot avoid direct manipulation
of de Bruijn indices when defining the semantics of scope extrusion;
cofinite quantification provides no benefits when working under
binders; nominal approaches require explicitly giving
and validating sets of free names during scope extrusion;
\end{quotation}

>>>>

This is the challenge most closely related to POPLMark,
since it concerns the properties of binders, whose encoding has been
extensively studied with respect to $\lambda$-calculi. Process calculi
present additional challenges, typically including several
different binding constructs: inputs bind a received name or value,
recursive processes bind recursion variables, and restrictions bind
names. The first two act similarly to the binders known from
$\lambda$-calculi, but restrictions may be more challenging due to
scope extrusion.
Scope extrusion requires reasoning about free variables, so approaches that identify \(\alpha\)-equivalent processes cannot be directly applied.

Given those peculiarities, the syntax and semantics of $\pi$-calculi have been
mechanised from an early age (see~\cite{Melham1994}) with many proof
assistants and in so many encoding styles that it would take too long to
review.  They range from concrete encodings based on named syntax
\cite{Melham1994} to basic de Bruijn~\cite{Hirschkoff1997, Perera2018} and locally nameless
representation %~\cite{Chargueraud2012}
(\eg~\cite{Castro2020}).
Nominal approaches are also common (see~\cite{Bengtson2009}), but they
may be problematic in proof assistants based on dependent types.
Another approach is shallow embeddings~\cite{Castro-Perez2021}, which avoids the need to explicitly represent names.
The case study \cite{AmbalLS21} compares four approaches to encoding
binders in Coq as a first step towards developing tools for working
with higher-order process calculi.  They found that working directly
with de Bruijn indices was easiest and shortest since the existing
approaches developed for $\lambda$-calculus binders do not work well
with scope extrusion.
